\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Damped Harmonic Oscillator\\}

\author{Authors: Waqar Awan and Dr. Spencer Smith }

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Fri Jan 19 & Waqar Awan(s) & Initial Document\\
\bottomrule
\end{tabularx}
\end{table}

\section{Problem Statement}

\subsection{Problem}
This project focuses on the physics of a damped harmonic oscillator, a concept in physics and engineering. 
It involves a mass-spring system, where the mass is subject to both a restoring force from the spring and a damping force. 
Understanding this system is crucial because it's a simplified model for many real-world phenomena like vehicle suspension systems and building responses to earthquakes.

\subsection{Inputs and Outputs}

\begin{itemize}
    \item \textbf{Input:} \begin{enumerate}
        \item Mass of the oscillator(m)
        \item Damping Coefficient(b)
        \item Spring constant(k)
        \item Displacement(x)
        \item Velocity(v)
        \item External force(if any)
    \end{enumerate}

    \item \textbf{Output:} \begin{enumerate}
        \item Time Evaluation
        \item Displacement and velocity of the mass as a function of time
        \item System response when under damped, critically damped, and over damped
        \item Amplitude
        \item Frequency
    \end{enumerate}
\end{itemize}

\subsection{Stakeholders}

\begin{itemize}
    \item Educators and students in physics and engineering disciplines.
    \item Developers of simulation software for physical systems.
    \item Industries dealing with oscillatory and vibration damping systems.
\end{itemize}

\subsection{Environment}

\begin{itemize}
    \item \textbf{Hardware:} \begin{enumerate}
        \item \textbf{Development Machine:} A computer with sufficient processing power and memory (RAM) to handle development tasks. Ideally, a multi-core processor and at least 4GB of RAM.
        \item \textbf{Testing Devices:} Smart devices like laptop and smartphone for testing correctness of the results and software interfaces.
    \end{enumerate}

    \item \textbf{Software:} \begin{enumerate}
        \item Involves computational tools for solving differential equations.
        \item Graphical tools for illustrating the system's behavior.
    \end{enumerate}
\end{itemize}

\section{Goals}
The main goals of this project is to:
\begin{itemize}
    \item Create a simulation model that accurately represents the behavior of a damped harmonic oscillator in various scenarios.
    \item Facilitate the understanding of damping effects on oscillatory systems through interactive and visual tools.
    \item Enhance educational understanding of damped oscillatory systems.
    \item Simulate real-time data and mathematical derivation.
    \item Design tools to allow user to create and save custom scenarios, and do comparative analysis.
\end{itemize}

\section{Stretch Goals}

\begin{itemize}
    \item Extend the model to include non-linear damping effects.
    \item Integrate real-time experimental data for comparison with simulations.
    \item Develop an augmented reality application to visualize oscillations in a physical environment.
\end{itemize}

\end{document}